Think deep for reef resilience

### 2025-07-03 paper/paper_draft.qmd
Add text on DHW timeseries plot

Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus visual further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 GCM (intermediate ECS scenario). Results for the additional GCMs are displayed in the supplementary material. However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-trajectories).

@@

![Reef relative coral cover timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#fig-gcm-trajectories width=`{julia} timeseries_width`}

@@

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#sfig-gcm-trajectories width=`{julia} timeseries_width`}

>>>>

Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus visual further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 GCM (intermediate ECS scenario). Results for the additional GCMs are displayed in the supplementary material. However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).

Under each GCM, in all management areas, low, medium and high cluster reefs have low differences between DHW trajectories (@sfig-gcm-dhw-trajectories). The highest peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHW timeseries occur under ACCESS-CM2.

@@

![Reef relative coral cover timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories width=`{julia} timeseries_width`}

@@

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories width=`{julia} timeseries_width`}
